Plots_manuscript_G_BLUP

### 2020-10-02 R/Plots_manuscript_G_BLUP.Rmd
Start manuscript v0.4 with FT genes from Xiaoyu incorporated

log10p_long %>% arrange(log10p) %>%
  group_by(sites, subpop, phe) %>%
  slice(1) %>%
  arrange(sites, subpop, phe) %>%
  mutate(pval = 10^-log10p)
```

@@

annos_df %>% 
  arrange(desc(`FDR Adjusted p value`)) %>%
  group_by(sites, subpop, phe) %>%
  slice(1) %>%
  arrange(sites, subpop, phe) %>%
  filter(sites %in% c("eight_sites", "tx_sites", "north_sites") & !(phe %in% c("GR50", "cgdd_12c_10d", "FL50", "crain_1d", "crain_gr2fl"))) 
  mutate(pval = 10^-log10p)
```

@@

qtlplot: Significant QTL for flowering in fourway cross.
```{r}
annos_df
ft_annos
osgene_ft_key

>>>>

log10p_long %>% arrange(log10p) %>%
  group_by(sites, subpop, phe) %>%
  slice(1) %>%
  arrange(sites, subpop, phe) %>%
  mutate(pval = 10^-log10p) %>%
  arrange(pval)
```

@@

annos_df %>% 
  arrange(desc(`FDR Adjusted p value`)) %>%
  group_by(sites, subpop, phe) %>%
  slice(1) %>%
  arrange(sites, subpop, phe) %>%
  filter(sites %in% c("eight_sites", "tx_sites", "north_sites") & !(phe %in% c("GR50", "cgdd_12c_10d", "FL50", "crain_1d", "crain_gr2fl")) & !subpop %in% c("Gulf_and_Midwest")) %>%
  arrange(`FDR Adjusted p value`)

```
# Get all SNPs above FDR from server.
phe %in% c("dyln_fl50", "cgdd_12c_gr2fl", "FL50")
sites %in% c("eight_sites", "tx_sites", "north_sites")
```{r}
phe_v <- c("dyln_fl50", "cgdd_12c_gr2fl", "FL50")
site_v <- c("eight_sites", "tx_sites", "north_sites")
i=1
j=1
gwas_FDR <- tibble()
for(i in seq_along(phe_v)){
  for(j in seq_along(site_v)){
  gwas_files <- list.files(path = paste0("./", site_v[j]), pattern = paste0("GWAS_datatable_", phe_v[i]))
  for(k in seq_along(gwas_files)){
    gwas1 <- readRDS(file.path(site_v[j], gwas_files[k])) %>%
      filter(FDR_adj < 0.1) %>%
      mutate(sites = site_v[j],
             phe = phe_v[i],
             gwas = gwas_files[k])
    gwas_FDR <- bind_rows(gwas_FDR, gwas1)
  }
}
}
saveRDS(gwas_FDR, file = "Univariate_G_BLUP_27_flowering_GWAS_SNPs_above_FDR10per.rds")
```

# FDR GWAS hits
```{r}
gwas_fdr <- read_rds("../analysis/gwas/BLUPs/Univariate_G_BLUP_27_flowering_GWAS_SNPs_above_FDR10per.rds")

gwas_fdr <- gwas_fdr %>%
  mutate(subpop = case_when(grepl("8\\.8M", gwas) ~ "Midwest",
                              grepl("10\\.3M", gwas) ~ "Gulf",
                              grepl("12\\.1M", gwas) ~ "Gulf_and_Midwest"),
         Pos_Mb = round(POS/10000)/100,
         POS_bin = round(Pos_Mb*100/2),
         Pos_Mb1 = round(Pos_Mb, digits = 1)) %>%
  filter(!(subpop == "Midwest" & between(log10p, 9.242223, 9.242225)) & !(subpop == "Midwest" & between(log10p, 12.466318, 12.46632)))

gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & phe %in% c("dyln_fl50", "cgdd_12c_gr2fl")) %>%
  group_by(sites, phe, subpop) %>%
  tally()

gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & phe %in% c("dyln_fl50", "cgdd_12c_gr2fl")) %>%
  group_by(CHR, POS) %>%
  tally() %>% arrange(desc(n))

gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & phe %in% c("dyln_fl50", "cgdd_12c_gr2fl")) %>%
  group_by(CHR, Pos_Mb1, POS_bin) %>%
  tally() %>% arrange(desc(n))
annos_plot1
ft_annos

gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & phe %in% c("dyln_fl50", "cgdd_12c_gr2fl")) %>%
  group_by(CHR, POS_bin) %>%
  tally() %>% arrange(desc(n))

gwas_fdr %>%
  group_by(log10p) %>%
  tally() %>% arrange(desc(n))
```
## Upset plot FDR
```{r}
fdr_upset <- gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & phe %in% c("dyln_fl50", "cgdd_12c_gr2fl")) %>%
  select(sites, subpop, phe, CHR, POS_bin) %>%
  unite(col = "GWAS", sites, subpop, phe) %>%
  unite(col = "CHR_POS", CHR, POS_bin) %>%
  mutate(Sig = TRUE) %>%
  complete(GWAS, CHR_POS, fill = list(Sig = FALSE)) %>%
  group_by(GWAS, CHR_POS, Sig) %>%
  slice(1) %>%
  pivot_wider(names_from = GWAS, values_from = Sig)
upset_v0 <- names(fdr_upset)[2:ncol(fdr_upset)]
freqplot_u <- upset(data = fdr_upset, intersect = upset_v0, 
      name="20kb region associations by univariate GWAS",
      base_annotations=list(
        'Intersection size'=intersection_size(text_aes=aes(label=paste0(round(intersection_size/nrow(fdr_upset) * 100), '%')))),
      min_size = 10,
      width_ratio = 0.125,
      themes=upset_modify_themes(
        list(
            'overall_sizes'=theme(axis.text.x=element_text(angle=45, hjust =1))
        ))) +
  labs(caption = "Number of 20kb windows with a significant GWAS hit.")
save_plot(filename = "../writeup/figures/Upset_plot_20kb_sig_allele_freq.png", plot = freqplot_u, base_height = 3)
```

Check out various smaller plots
```{r}
fdr_upset <- gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & !phe %in% c("FL50")) %>%
  select(sites, subpop, phe, CHR, POS_bin) %>%
  unite(col = "GWAS", sites, subpop, phe) %>%
  unite(col = "CHR_POS", CHR, POS_bin) %>%
  mutate(Sig = TRUE) %>%
  complete(GWAS, CHR_POS, fill = list(Sig = FALSE)) %>%
  group_by(GWAS, CHR_POS, Sig) %>%
  slice(1) %>%
  pivot_wider(names_from = GWAS, values_from = Sig)
upset_v0 <- names(fdr_upset)[2:ncol(fdr_upset)]
upset(data = fdr_upset, intersect = upset_v0, 
      name="20kb region associations by univariate GWAS",
      base_annotations=list(
        'Intersection size'=intersection_size()),
      min_size = 0,
      width_ratio = 0.125,
      themes=upset_modify_themes(
        list(
            'overall_sizes'=theme(axis.text.x=element_text(angle=45, hjust =1))
        ))) +
  labs(caption = "Number of 20kb windows with a significant GWAS hit.")

three_uni_gwas <- gwas_fdr %>%
  filter(subpop %in% c("Midwest", "Gulf") & !phe %in% c("FL50")) %>%
  group_by(sites, subpop, phe, CHR, POS_bin) %>%
  tally() %>%
  group_by(CHR, POS_bin) %>%
  summarise(count = n()) %>% arrange(desc(count)) %>%
  filter(count > 2)

three_uni_gwas %>%
  arrange(CHR, POS_bin) %>%
  left_join(ft_annos, by = c("CHR" = "seqid", "POS_bin")) %>%
  select(CHR, Pos_Mb, everything())

gwas_fdr %>%
  filter(log10p > 7) %>%
  filter(subpop %in% c("Gulf", "Midwest") & !phe %in% c("FL50")) %>%
  group_by(sites, subpop, phe, CHR, POS_bin) %>%
  tally() %>%
  group_by(CHR, POS_bin) %>%
  summarise(count = n()) %>%
  left_join(ft_annos, by = c("CHR" = "seqid", "POS_bin")) %>%
  select(CHR, Pos_Mb, everything()) %>%
  filter(!is.na(OsGene) | !is.na(AtGene)) %>%
  left_join(osgene_ft_key, by = c("OsGene" = "Symbol")) # 93 out of 3148 rows contain candidates
(9/223)/(1599/83260) # all regions log10p > 7   OR 2.1
(26/793)/(1599/83260) # all regions log10p > 6   OR 1.7
(65/2240)/(1599/83260) # all regions log10p > 5   OR 1.51
(10/280)/(1599/83260) # all regions FDR 1%
(43/1393)/(1599/83260) # all regions FDR 5%
(95/3137)/(1599/83260) # all regions FDR 10%

(10/268)/(1599/83260)
(81/2551)/(1599/83260) # OR north sites 1.65
(8/420)/(1599/83260) # OR tx sites 0.99! NS!
(16/463)/(1599/83260) # OR all sites 1.80
(95/3137)/(1599/83260)
fisher.test(matrix(c(95, 1599, 3137, 83260), nrow = 2))
fisher.test(matrix(c(16, 1599, 463, 83260), nrow = 2))
fisher.test(matrix(c(81, 1599, 2551, 83260), nrow = 2))
fisher.test(matrix(c(8, 1599, 420, 83260), nrow = 2))
```
For the Midwest subpop, there aren't sig assoc for dyln in TX. Just CGDD.
For the Gulf, there aren't sig assoc for CGDD in TX. Just dyln.
For G&M in Texas, 61% signals are just for dyln. 33% both dyln & CGDD. 6% CGDD.
For G&M in North, 76% signals are just for CGDD. 20% both. 2% dyln.

2K 52: FT
3K 19 FTL10

```{r}

@@

qtlplot: Significant QTL for flowering in fourway cross.
```{r}
annos_df %>%
  arrange(desc(`FDR Adjusted p value`))
ft_annos
osgene_ft_key
